\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-17 pldi/draft.tex
Comments on the one-liners evaluation
Final one-liner results with auto split too

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Parallel + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

@@

>>>>

    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.24\textwidth}
      \centering
      \includegraphics[width=\textwidth]{\detokenize{./figs/bigrams_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
      (ii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iii) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (iv) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

\kk{Remember to mention that for spell and bigrams we dont show other
  parallel because they are all close to 1 (no speedup).}

@@

\kk{It is visible that the automatic split is slightly worse than the
  manual one in most cases (because it doesn't utilize task-based
  parallelism).}
